---
title: 'Building a statistical model of reaction times to automation failures.'
author: "Callum Mole"
output:
  html_document:
    df_print: paged
  html_notebook:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
---

## Introduction

This document steps through the statistical model building for takeover reaction times in a silent failure experiment, pre-reg can be found at https://osf.io/mydfw. We are primarily interested in how cognitive load affects reaction times at different levels of failure.

First we load the data.

```{r Load preliminaries, include=FALSE, warning=FALSE}

library("tidyverse")
library("brms")
library("tidybayes")

```


```{r Load data, echo=FALSE, message=FALSE, warning=FALSE}

#set working directory to folder that hosts the binary files.
setwd("C:/git_repos/Orca18_Analysis/Post-Processing/")

balanced_RTs <- read_csv("balanced_RTs.csv")  

#add failure factor.
balanced_RTs$failure <- factor(balanced_RTs$simTTLC, labels = c("1","2","3","4"))

#get rid of premature takeovers. Not interested in those.
balanced_RTs <- balanced_RTs %>% 
  filter(premature == 0)

knitr::kable(head(balanced_RTs))


```
Let's plot a scatter plot to get an idea of the behaviour. We draw trend lines through the medians of each factor.

```{r scatter plots, echo=FALSE, message=FALSE, warning=FALSE}

#median data frame.
med_RTs <- balanced_RTs %>% 
  group_by(failure, cogload) %>% 
  summarise(RT = median(RT))

dodge <- position_dodge(width=0.1)  
ggplot(balanced_RTs, aes(x = failure, y= RT, colour = cogload, group = cogload)) +
  geom_point(alpha = .1, position = dodge) +
  geom_line(data = med_RTs, size = 1, position = dodge) +
  geom_point(data = med_RTs, size =2, position = dodge) +
  scale_colour_brewer(palette = "Set1")
  
```



```{r load and plot random_RTs, echo=FALSE, message=FALSE, warning=FALSE}

random_RTs <- read_csv("random_RTs.csv")  

#get rid of premature takeovers. Not interested in those.
random_RTs <- random_RTs %>% 
  filter(premature == 0)

data_RTs <- full_join(balanced_RTs, random_RTs)


```


```{r calc offset, echo=FALSE, message=FALSE, warning=FALSE}

ttlc_from_offset <- function(b, w = 1.5, r = 60, v = 8){
  b = b / 180 * pi
  
  ttlc = sqrt(w*(2*r + sign(b)*w)/(abs(b)*r*v))
}
data_RTs <- data_RTs %>% 
  mutate(ttlc_calc = ttlc_from_offset(sab))


balanced_RTs <- balanced_RTs %>% 
  mutate(ttlc_calc = ttlc_from_offset(sab))


```



```{r m3 random intercept and slope, echo=FALSE, message=FALSE, warning=FALSE}

form <- bf(RT | trunc(lb = 0, ub = 10) ~ failure * cogload, sigma ~ failure)
#my_form <- bf(RT ~ ttlc_calc * cogload + (1 + ttlc_calc + cogload | ppid), shape ~ (1 + ttlc_calc | ppid), center = FALSE)
m4.1 <- brm(data = balanced_RTs, formula = form, 
          family = gaussian(),
          iter = 5000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

pp_check(m4.1)

m4_predict <- balanced_RTs  %>%
  add_predicted_draws(m4.1) 
  #ggplot(aes(x = RT, y = .prediction)) +
  #geom_point(alpha = .5)

###plot predicted values
### plot the distributions of the balanced RTs
#retrieves ttlc_calc balanced levels.
#ribbon plot
ggplot(balanced_RTs, aes(x = ttlc_calc, y= RT)) +
  stat_lineribbon(data = m4_predict, aes(y = .prediction), .width = c(.99, .95, .50), alpha = .5, col = "magenta", fill = "red") +
  xlim(0,15) + ylim(0,10) +
  geom_point(alpha = .25, col = "black")


m4_balanced_predictions <- filter(m4_predict, ttlc_calc %in% ttlc_calc_levels)

ggplot(data = balanced_RTs) +
  geom_density(aes(x = RT), col = "red", alpha = .5) +
  geom_density(data = m4_balanced_predictions, aes(x = .prediction), alpha = .8, col = "blue") +
  facet_wrap(~ttlc_calc, scales = "free") +
  ylab("density")

ggplot(data = balanced_RTs) +
  geom_density(aes(x = RT), col = "red", alpha = .5) +
  geom_density(data = m4_predict, aes(x = .prediction), alpha = .8, col = "blue") +
  facet_wrap(~ttlc_calc, scales = "free") +
  ylab("density")

```