---
title: 'Building a statistical model of reaction times to automation failures.'
author: "Callum Mole"
output:
  html_document:
    df_print: paged
  html_notebook:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
---

## Introduction

This document steps through the statistical model building for takeover reaction times in a silent failure experiment, pre-reg can be found at https://osf.io/mydfw. We are primarily interested in how cognitive load affects reaction times at different levels of failure.

First we load the data.

```{r Load preliminaries, include=FALSE, warning=FALSE}

library("tidyverse")
library("brms")
library("tidybayes")
library("wesanderson")
library("cowplot")

```

```{r, load data}

REFIT = TRUE #whether to refit models.


setwd("C:/git_repos/Orca18_Analysis/Post-Processing/")

#load steergaze data


#steergazedata <- read_csv("../Data/Orca19_collated_steering.csv")  
#saveRDS(steergazedata, "../Data/Orca19_collated_steering.rds")
steergazedata <- readRDS("../Data/Orca19_collated_steering.rds")  


steergazedata <- steergazedata %>% 
  rename(swv = swa) %>% 
  mutate(swa = swv * 90)

#mirror data
steergazedata <- steergazedata %>% 
  mutate(world_x_mirrored = if_else(bend == -1, world_x * -1, world_x),
         swa_mirrored = if_else(bend == -1, swa * -1, swa),
         swv_mirrored = if_else(bend == -1, swv * -1, swv),
         sb_mirrored = if_else(bend == -1, steeringbias * -1, steeringbias))



ttlc_from_offset <- function(b, w = 1.5, r = 60, v = 8){
  b = b / 180 * pi
  
  ttlc = sqrt(w*(2*r + sign(b)*w)/(abs(b)*r*v))
}

steergazedata <- steergazedata %>% 
  mutate(ttlc_calc = ttlc_from_offset(sab))

#add RT and disengage flag.
disengage_RT <- function(onsettime, timestamp_trial, autoflag){
  
  #pick first frame where autoflag == false, then take the timestamp and minus the onset_time
  auto_false <- which(autoflag == "FALSE")
  disengage_index <- first(auto_false)
  disengage_trialtime <- timestamp_trial[disengage_index]
  onset_time <- first(onsettime)
  RT <- disengage_trialtime - onset_time #can be negative
  return(RT)
  
}

#calculate RT
steergazedata <- steergazedata  %>% 
  group_by(ppid, sab, cogload, trialn) %>% 
  mutate(RT = disengage_RT(onsettime, timestamp_trial, autoflag),
         disengaged = ifelse(is.na(RT), 0, 1) #whether or not they actually took over.
  )

#create unique trial id
steergazedata <- steergazedata %>% 
  mutate(trialid = paste(ppid, cogload, trialn, sep = "_"))

steergazedata$cogload <- as.factor(steergazedata$cogload)


#rename cogload factors so that it ameks sense
steergazedata$cogload<- plyr::mapvalues(steergazedata$cogload, from = c("None", "Middle"), to = c("noload", "load"))





#we now have two data frames. "balanced_steerdata" and "random_steerdata"
data_RTs <- steergazedata  %>% 
  ungroup() %>% 
  group_by(ppid, cogload, trialn) %>% 
  summarize(RT = first(RT),
            disengaged = first(disengaged), #whether or not they actually took over.
            premature = ifelse(RT <= 0, 1, 0),
            sab = first(sab),
            onsettime = first(onsettime),
            design = first(design),
            simTTLC = first(simulated_ttlc),
            ttlc_calc = first(ttlc_calc))

```


Let's plot a scatter plot to get an idea of the behaviour. We draw trend lines through the medians of each factor.

```{r scatter plots, echo=FALSE, message=FALSE, warning=FALSE}

#median data frame.
med_RTs <- data_RTs %>% 
  filter(design == "balanced", disengaged == 1) %>%
  group_by(simTTLC, cogload) %>% 
  summarise(RT = median(RT))

dodge <- position_dodge(width=0.1)  

p <- ggplot(filter(data_RTs, design == "balanced"), aes(x = simTTLC, y= RT, colour = cogload, group = cogload)) +
  geom_point(alpha = .1, position = dodge) +
  geom_line(data = med_RTs, size = 1, position = dodge) +
  geom_point(data = med_RTs, size =2, position = dodge) +
  scale_colour_brewer(palette = "Set1")

#ggsave('meds.png', p,  device="png", width=18, height= 8.5, units = "cm", dpi=300, type="cairo")

#steergazedata %>% 
#  ungroup() %>% 
#  filter(design == "random") %>% 
#  summarise(min(autofile_i))
  
```



```{r load and plot random_RTs, echo=FALSE, message=FALSE, warning=FALSE}



ticks <- data_RTs %>% 
  filter(design == "balanced") %>% 
  ungroup() %>% 
  mutate(simTTLC = round(simTTLC, digits = 1)) %>% 
  select(simTTLC) %>% 
  unique(.)
  
  

p <- ggplot(filter(data_RTs, premature == 0, disengaged == 1), aes(x = simTTLC, y= RT, colour = cogload, group = cogload)) +
  geom_point(alpha = .1, position = dodge) +
  geom_line(data = med_RTs, size = 1, position = dodge) +
  geom_point(data = med_RTs, size =2, position = dodge) +
  scale_colour_brewer(palette = "Set1") +
  theme_classic() +
  scale_x_continuous(breaks = ticks$simTTLC, labels = ticks$simTTLC)

print(p)

ggsave('meds_full.png', p,  device="png", width=18, height= 8.5, units = "cm", dpi=300, type="cairo")

max(data_RTs$RT)

data_RTs <- mutate(data_RTs, time_remaining = 15 - onsettime,
                   early = time_remaining - RT)

head(filter(data_RTs, early < .1))

ggplot(data_RTs, aes(x = time_remaining, y = time_remaining - RT)) + geom_point()

```


```{r, plot density}

p_dens <- ggplot(filter(data_RTs, design == "balanced", premature == 0, disengaged == 1), aes(x = RT, group = factor(sab), colour = factor(sab))) +
  geom_density(alpha = .8) +
  xlim(c(0,10)) +
  scale_colour_manual(values = rev(wes_palette("BottleRocket2",n=4)), name = "Failure TTLC (s)", labels = c("2.23", "4.68", "7.1", "9.5")) +
  xlab(expression("RT"["takeover"]*" (s)")) + theme_classic()

print(p_dens)

ggsave('dens.png', p_dens,  device="png", width=18, height= 8.5, units = "cm", dpi=300, type="cairo")


```

```{r, plot variance}

#variance data frame.
var_RTs <- data_RTs %>% 
  filter(disengaged == 1, premature == 0) %>% 
  group_by(design, ttlc_calc, cogload) %>% 
  summarise(var = var(RT))

head(var_RTs)

#dodge <- position_dodge(width=0.1)  
p_var <- ggplot(data = filter(var_RTs, design == "balanced"), aes(x = ttlc_calc, y= var, colour = cogload, group = cogload)) +
  geom_point(alpha = 1) +
  geom_line() +
  geom_point(data = filter(var_RTs, design == "random"), aes(x = ttlc_calc, y= var, colour = cogload, group = cogload), alpha = .3) +
  scale_colour_brewer(palette = "Set1") +
  ylim(0,1.5) + theme_classic()

print(p_var)
ggsave('var.png', p_var,  device="png", width=18, height= 8.5, units = "cm", dpi=300, type="cairo")

```
```{r, check cogload relationship across ttlc}

meds <- data_RTs %>% 
  filter(design == "balanced") %>% 
  group_by(ppid, ttlc_calc, cogload) %>% 
  summarise(medRT = median(RT))


head(meds)
cogload_diff <- meds %>% 
  group_by(ppid, ttlc_calc) %>% 
  summarise(diff = medRT[1] - medRT[2],
            val = diff/medRT[2],
            noload = medRT[2]) 

med_trend <- cogload_diff %>% group_by(ttlc_calc) %>% summarise(meddiff = median(diff, na.rm = TRUE))

ggplot(cogload_diff, aes(x = val)) + 
  geom_histogram(alpha = .5) 

ggplot(cogload_diff, aes(x = noload, y = diff, group = ppid, colour = factor(ppid))) + 
  geom_point(alpha = .5) +
  #geom_line(data = med_trend, aes(x = ttlc_calc, y = meddiff))
  geom_line(alpha = .7)


```


```{r, check inverse relationship}

data_RTs <- data_RTs %>% mutate(inv_RT = 1/RT, inv_TR = 1/time_remaining, inv_ttlc = 1/ttlc_calc)
ggplot(filter(data_RTs, premature == 0), aes(x =ttlc_calc, y= RT, colour = cogload, group = cogload)) +
  geom_point(alpha = .8) +
  facet_wrap(~ppid)



```



```{r checking best response distribution, echo=FALSE, message=FALSE, warning=FALSE, eval = FALSE}

#init_f <- function () list(Intercept = rnorm(1, 15, 2.), shape = max(.01,rnorm(1, 3, 1)), scale =max(.01,rnorm(1, 3, 1))  )
#we have non-linear variance and slightly non-linear RT -> sab mapping, so taking the log-log forces the data into a linear space.

data_RTs <- data_RTs %>% mutate(log_RT = log(RT), log_TR = log(time_remaining), log_ttlc = log(ttlc_calc))

ggplot(data_RTs, aes(x = log_ttlc, y= log_RT, colour = cogload, group = cogload)) +
  geom_point(alpha = .8, position = dodge) +
  facet_wrap(~ppid)
  

ggplot(filter(data_RTs, disengaged == 1), aes(x = log(ttlc_calc), y= var(log_RT))) + geom_point() #also variance is homogenous.

ggplot(data = data_RTs) +
  geom_histogram(aes(x = RT), fill = "red", alpha = .2) +
  #geom_density(data = m0.weib_pred, aes(x = log(.prediction)), alpha = .8, col = "blue") +
  facet_wrap(~ttlc_calc, scales = "free_y") +
  geom_vline(aes(xintercept = time_remaining)) +
  ylab("density")

#ggplot(data = data_RTs, aes(x = ttlc_calc, y = sab, color = onsettime, size = sab)) + geom_point()

#hist(log(fail$RT))


#form <- bf(RT | trunc(ub = time_remaining) ~ ttlc_calc*cogload + (1 + ttlc_calc*cogload | ppid))
log_form <- bf(log_RT | trunc(ub = log_TR) ~ log_ttlc+cogload + (1 + log_ttlc+cogload | ppid), sigma ~ (1 | ppid))
#log_form_onset <- bf(log_RT | trunc(ub = log_TR) ~ log_ttlc*cogload + onsettime + (1 + log_ttlc*cogload | ppid), sigma ~ (1 | ppid))

tofit <- filter(data_RTs, premature == 0 | is.na(premature)) #include the NA responses
tofit <- filter(tofit, (early > 0 | is.na(early))) #there is one trial where they have taken over after the trialelapsed, and it has been recorded.
tofit %>% 
  mutate(diff = log_TR - log_RT) %>% 
  filter(diff < 0) %>% 
  head()

#let's use families where the canonical link is the identity function for ease of interpretation. 
tofit <- tofit %>% mutate(log_ttlc = round(log_ttlc, 2),calc_ttlc = round(calc_ttlc, 2))
only_responses <- filter(tofit, disengaged == 1)
m0.gauss_resp <- brm(data = only_responses, formula = log_form,
                family = gaussian(),
                iter = 5000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

m0.gauss <- brm(data = tofit, formula = log_form,
                family = gaussian(),
                iter = 5000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

#CM: when the other predictors are log space it is difficult to do it additve.
#m0.gauss_onset <- brm(data = tofit, formula = log_form_onset,
#                family = gaussian(),
#                iter = 5000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

summary(m0.gauss)
summary(m0.gauss_resp) #it doesn't matter if you include the RTs as NAs or not.
#summary(m0.gauss_onset)
pp_check(m0.gauss)
pp_check(m0.gauss_resp)
#pp_check(m0.gauss_onset)
#loo(m0.gauss, m0.gauss_onset)
#loo_model_weights(m0.gauss, m0.gauss_onset)

marginal_effects(m0.gauss)

```

```{r, useful functions}




ttlc_calc <- seq(1, to = 15, by = .1)
ppid <- 1:20
cogload <- c("noload","load")
pred_list <- expand_grid(ttlc_calc, ppid, cogload)


create_predictions <- function(mod, condition_list){
  preds <- predict(mod, newdata=condition_list, summary=TRUE, probs = c(.005, 0.025, .25, .75, 0.975, .995), transform = "exp")     
  preds <- cbind(condition_list,preds) #add the condition values
  return(preds)
}

plot_ribbon <- function(dat, preds, fname, x, y){

  p <- ggplot(preds, aes_string(x = x)) +
    geom_line(aes(y = Q0.5), col = "blue", alpha = .2) +
    geom_line(aes(y = Q99.5), col = "blue", alpha = .2) +
    geom_line(aes(y = Q2.5), col = "blue", alpha = .5) +
    geom_line(aes(y = Q97.5), col = "blue", alpha = .5) +
    geom_line(aes(y = Q25), col = "blue", alpha = .75) +
    geom_line(aes(y = Q75), col = "blue", alpha = .75) +
    geom_line(aes(y = Estimate), col = "lightblue") +
    geom_point(data = dat, aes_string(x = x, y = y), alpha = .5, col = "black") +
  facet_wrap(~ppid) + ggsave(fname)
  
  return(p)
}


plot_hist <- function(mod, dat, x, xint){
  
  pred <- dat  %>%
  add_predicted_draws(mod)
  
  p <- ggplot(data = pred) +
  geom_histogram(aes_string(x = x), fill = "red", alpha = .4) +
  geom_histogram(aes(x = exp(.prediction)), alpha = .4, fill = "blue") +
  facet_wrap(~ttlc_calc, scales = "free_y") +
  geom_vline(aes_string(xintercept = xint)) +
  ylab("density")
  
  return(p)
}

```


```{r, non-linear model}

data_RTs <- data_RTs %>% mutate(log_RT = log(RT), log_TR = log(time_remaining), log_ttlc = log(ttlc_calc))
only_responses <- filter(data_RTs, disengaged == 1, premature == 0, early > 0)

#log(RT) = log(ttlc+cogload) *sigma


nl_bf <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload)), 
            b1 ~1, b2 ~ 1, nl = TRUE)


prior1 = c(prior(normal(0, 4), nlpar = "b1"),
    prior(normal(0, 4), nlpar = "b2"))

#rows containing nas are excluded.
nl1 = brm(data = only_responses, formula = nl_bf, prior = prior1, family = gaussian())


summary(nl1)
plot(nl1)
pp_check(nl1)


p <- plot_ribbon(nl1, only_responses, 'nl_ribbon.png', 'ttlc_calc','RT')
print(p)
p1<-plot_hist(nl1, only_responses, 'nl_hist.png', 'RT', 'time_remaining')
print(p1)




nl_bf_sig <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload)), sigma ~ (1 | ppid),
            b1 ~1, b2 ~ 1, nl = TRUE)

nl1_sig = brm(data = only_responses, formula = nl_bf_sig, prior = prior1, family = gaussian())




summary(nl1_sig)
loo(nl1, nl1_sig)
loo_model_weights(nl1, nl1_sig)
pp_check(nl1_sig)
#print(plot_ribbon(nl1_sig, only_responses, 'nl1sig_ribbon.png', 'ttlc_calc','RT'))


nl_bf_sig_inter <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload) + (b3 * cogload*ttlc_calc)), sigma ~ (1 | ppid),
            b1 ~1, b2 ~ 1, b3 ~ 1, nl = TRUE)

prior3 = c(prior(normal(0, 3), nlpar = "b1"),
    prior(normal(0, 3), nlpar = "b2"),
    prior(normal(0, 3), nlpar = "b3"))

nl1_sig_inter = brm(data = only_responses, formula = nl_bf_sig_inter, prior = prior3, family = gaussian(),
                     iter = 5000, cores = 4, refresh = 500, chains = 4, warmup = 1000, control = list(adapt_delta = 0.90))


summary(nl1_sig_inter)
pp_check(nl1_sig_inter)
#we could also independently predict the spread, but in a lognormal these spreads cannot be interpreted independently of the means it gets a bit messy.





nl_bf_varsig <- bf(log_RT | trunc(ub = log_TR) ~ log((b1 * ttlc_calc) + (b2 * cogload) + (b3*ttlc_calc*cogload)),  sigma ~ (1 | ppid),
            b1 ~ 1 + (1 | ppid), b2 ~ 1 + (1 | ppid), b3 ~ 1 + (1 | ppid), nl = TRUE)

#could have tighter priors to help with the initialisation.
prior3 = c(prior(normal(2,2), nlpar = "b1"),
    prior(normal(2, 2), nlpar = "b2"),
    prior(normal(2, 2), nlpar = "b3"))

#if the location is below 1 then log is negative and it won't initialise.
#some work needed here on the correct priors and initialisation formulas once initial draft is complete. 
if (REFIT == TRUE){
  nl_varsig = brm(data = only_responses, formula = nl_bf_varsig, prior = prior3, family = gaussian(), inits = c(1,1,1),
               iter = 10000, cores = 4, refresh = 500, chains = 1, warmup = 1000, control = list(adapt_delta = 0.99))
  save(nl_varsig, file ='MOD.rda')
} else {
  load('MOD.rda')
}




summary(nl_varsig)

pp_check(nl_varsig)


```

```{r, fig1 - visualising predictive intervals}

MOD <- nl_varsig
#Fig1, overall predictive intervals.
max(only_responses$ttlc_calc)
ttlc_calc <- seq(1, to = 13, by = .1)
log_TR <- 100
#ppid <- 1:20
cogload <- c("noload","load")
pred_list <- expand_grid(ttlc_calc, cogload, log_TR)
preds <- predict(MOD, newdata=pred_list, summary=TRUE, allow_new_levels = TRUE, probs = c(.005, 0.025, .25, .75, 0.975, .995), transform = "exp") %>% 
  cbind(pred_list) %>% 
  group_by(ttlc_calc) %>% 
  mutate(Estimate = mean(Estimate),
         Q0.5 = min(Q0.5),
         Q2.5 = min(Q2.5),
         Q25 = min(Q25),
         Q75 = max(Q75),
         Q97.5 = max(Q97.5),
         Q99.5 = max(Q99.5))

pred_col = "turquoise4"
data_col = "black"
ribbon <- ggplot(preds, aes(x = ttlc_calc)) +
  geom_line(aes(y = Q0.5), col = pred_col, alpha = .5, linetype = 2) +
    geom_line(aes(y = Q99.5), col = pred_col, alpha = .5, linetype = 2) +
    geom_line(aes(y = Q2.5), col = pred_col, alpha = .75, linetype = 2) +
    geom_line(aes(y = Q97.5), col = pred_col, alpha = .75, linetype = 2) +
    geom_line(aes(y = Q25), col = pred_col, alpha = 1, linetype = 2) +
    geom_line(aes(y = Q75), col = pred_col, alpha = 1, linetype = 2) +
    geom_line(aes(y = Estimate), col = pred_col) +
  geom_point(data = only_responses, aes(x = ttlc_calc, y= RT), alpha = .25, col = data_col) +
  theme_classic() +
  xlab("TTLC (s)") + ylab("RT (s)") + ylim(0,15)

print(ribbon)
ggsave("overall_predictiveintervals.png", plot = ribbon, dev = "png", width = 18, height = 8.5, units = "cm", dpi = 300, type = "cairo")
  



```

```{r, appendix plot for overlaid distributions}

#TODO: make plot prettier.
phist <- plot_hist(MOD, only_responses, 'RT', 'time_remaining')
ggsave("histogram_ppcheck.png", plot = phist, dev = "png", width = 18, height = 8.5, units = "cm", dpi = 300, type = "cairo")


```


```{r, Fig2 individual predictive intervals, across load.}


#Fig1, overall predictive intervals.
max(only_responses$RT)
ttlc_calc <- seq(1, to = 13, by = .1)
log_TR <- 100
ppid <- 1:20
cogload <- c("noload","load")
pred_list <- expand_grid(ttlc_calc, cogload, ppid, log_TR)
preds <- predict(MOD, newdata=pred_list, summary=TRUE, probs = c(.005, 0.025, .25, .75, 0.975, .995), transform = "exp") %>% 
  cbind(pred_list) %>% 
  group_by(ppid, ttlc_calc) %>% 
  mutate(Estimate = mean(Estimate),
         Q0.5 = min(Q0.5),
         Q2.5 = min(Q2.5),
         Q25 = min(Q25),
         Q75 = max(Q75),
         Q97.5 = max(Q97.5),
         Q99.5 = max(Q99.5))

ind_ribbon <- ggplot(preds, aes(x = ttlc_calc)) +
  geom_line(aes(y = Q0.5), col = pred_col, alpha = .5, linetype = 2) +
    geom_line(aes(y = Q99.5), col = pred_col, alpha = .5, linetype = 2) +
    geom_line(aes(y = Q2.5), col = pred_col, alpha = .75, linetype = 2) +
    geom_line(aes(y = Q97.5), col = pred_col, alpha = .75, linetype = 2) +
    geom_line(aes(y = Q25), col = pred_col, alpha = 1, linetype = 2) +
    geom_line(aes(y = Q75), col = pred_col, alpha = 1, linetype = 2) +
    geom_line(aes(y = Estimate), col = pred_col) +
  facet_wrap(~ppid) +
  geom_point(data = only_responses, aes(x = ttlc_calc, y= RT), alpha = .5, col = data_col) +
  theme_classic() +
  xlab("TTLC (s)") + ylab("RT (s)") + ylim(0,12)

print(ind_ribbon)
ggsave("pp_predictiveintervals.png", plot = ind_ribbon, dev = "png", width = 18, height = 15, units = "cm", dpi = 300, type = "cairo")

```


```{r, Fig3 estimation of mean effect on median}


ttlc_calc <- seq(1, to = 13, by = .1)
log_TR <- 100
cogload <- c("noload","load")
pred_list <- expand_grid(ttlc_calc, cogload, log_TR)
preds <- fitted(MOD, newdata=pred_list, summary=TRUE, re_formula = NA, probs = c(.005, 0.025, .25, .75, 0.975, .995)) %>% 
  cbind(pred_list) 

cols = c("#16bf81", "#c21756")
mn_ribbon <- ggplot(preds, aes(x = ttlc_calc, group = cogload, col = cogload)) +
 # geom_line(aes(y = exp(Q0.5)), alpha = .2, linetype = 2) +
#    geom_line(aes(y = exp(Q99.5)), alpha = .2, linetype = 2) +
    geom_line(aes(y = exp(Q2.5)), alpha = .5, linetype = 2) +
    geom_line(aes(y = exp(Q97.5)), alpha = .5, linetype = 2) +
#    geom_line(aes(y = exp(Q25)), alpha = .75, linetype = 2) +
#    geom_line(aes(y = exp(Q75)), alpha = .75, linetype = 2) +
    scale_colour_manual(values = cols) +
    geom_line(aes(y = exp(Estimate))) +
  theme_classic() +
  xlab("TTLC (s)") + ylab("RT (s)") + ylim(0,12) +
  theme(legend.position = c(0.2, 0.8))

print(mn_ribbon)

calc_hdis <- function(df){
  
  hdi <- df %>% 
  summarise(HDI2.5 = hdi(ct, credMass = .95)[1],
            HDI97.5 = hdi(ct, credMass = .95)[2],
            mn = mean(ct),
            AboveZero = mean(ct > 0),
            BelowZero = mean(ct < 0),
            hdi_95range = HDI97.5 - HDI2.5) %>% 
    ungroup()
  
  return(hdi)

}

#ln(RT) = N ( mu, sigma)
#mu = log(b1 + b2 + b3)
#RT med = exp(mu) #median of RT distribution
#RT med= b1 + b2 + b3
#the coefficients are in seconds units, and they can be interpreted as a direct effect on the median of the distribution

#plot distribution of main effects and interactions.
get_variables(MOD)
fixef_raw <- as.data.frame(fixef(MOD, summary = FALSE))
fixef_hdi <- as.data.frame(fixef(MOD, summary = TRUE, probs = c(0.025, 0.975)))

head(fixef_raw$b3_Intercept)
print(fixef_hdi)
#cogload
b2_hdi <- fixef_hdi["b2_Intercept",]

remove_yticks <-  theme(axis.text.y = element_blank(),
  axis.ticks.y = element_blank())

clfixplot <- ggplot() + 
  geom_histogram(data = fixef_raw, aes(x = -b2_Intercept), bins = 60, fill = "seagreen4", alpha = 1)+
  geom_segment(data=b2_hdi, aes(x=Q2.5*-1, y=0, xend=Q97.5*-1, yend=0), size=1) + 
  geom_point(data=b2_hdi, aes(x=Estimate*-1, y=0), size=2) +
  theme_classic() + 
  geom_vline(xintercept=0, linetype="dashed", col = "grey40") + 
  xlim(0, .5) + xlab("RT increase when loaded (s)") + ylab("") + remove_yticks
  
print(clfixplot)

#ttlc
b1_hdi <- fixef_hdi["b1_Intercept",]
ttlcfixplot <- ggplot() +
  geom_histogram(data = fixef_raw, aes(x = b1_Intercept), bins = 60, fill = "skyblue3", alpha = 1)+
  geom_segment(data=b1_hdi, aes(x=Q2.5, y=0, xend=Q97.5, yend=0), size=1) + 
  geom_point(data=b1_hdi, aes(x=Estimate, y=0), size=2) +
  theme_classic() + 
  geom_vline(xintercept=0, linetype="dashed", col = "grey40") +
  xlim(.4, .9) + xlab("RT increase with TTLC (s)") + ylab("") + remove_yticks

print(ttlcfixplot)
  
#cogload * ttlc
b3_hdi <- fixef_hdi["b3_Intercept",]
interplot <- ggplot() +
  geom_histogram(data = fixef_raw, aes(x = -b3_Intercept), bins = 60, fill = "turquoise4", alpha = 1)+
  geom_segment(data=b3_hdi, aes(x=Q2.5*-1, y=0, xend=Q97.5*-1, yend=0), size=1) + 
  geom_point(data=b3_hdi, aes(x=Estimate*-1, y=0), size=2) +
  theme_classic() +
  geom_vline(xintercept=0, linetype="dashed", col = "grey40") +
  xlim(-.2, .1) + xlab("Change in TTLC slope with added load (s)") + ylab("") +remove_yticks

print(interplot)


right_col <- plot_grid(ttlcfixplot, clfixplot, interplot, nrow = 3, labels = c("B","C","D"), label_size = 12)
full_grid <- plot_grid(mn_ribbon, right_col, ncol = 2, labels = c("A",""), label_size = 12, rel_widths = c(1,.75))
print(full_grid)

ggsave("population_coefficient_means.png", plot = full_grid, dev = "png", width = 18, height = 10, units = "cm", dpi = 300, type = "cairo")

```


```{r, effect on variance, eval = FALSE}

#ln(RT) = N (mu, sigma)
#log(sigma) = b_ttlc + b_noload + b_load
#sigma = exp(b_ttlc + b_noload + b_load...)
#effect on sigma on the log normal distribution cannot be considered in isolation.
#variance of ln distributed RT = [exp(sigma^2)-1]exp(2*mu + sigma^2)





```

```{r, Fig 4 - within pp variability}

#estimate hdi ranges for each person
#Fig1, overall predictive intervals.
max(only_responses$RT)
ttlc_calc <- seq(1, to = 13, by = .1)
log_TR <- 100
ppid <- 1:20
cogload <- c("noload","load")
pred_list <- expand_grid(ttlc_calc, cogload, ppid, log_TR)
pred_ranges <- predict(MOD, newdata=pred_list, summary=TRUE, probs = c(.005, 0.025, .25, .75, 0.975, .995), transform = "exp") %>% 
  cbind(pred_list) %>% 
  group_by(ppid, ttlc_calc, cogload) %>% 
  mutate(R99 = Q99.5 - Q0.5,
         R95 = Q97.5 - Q2.5,
         R50 = Q75 - Q25)

#cacl empirical ranges
emp_ranges <- only_responses %>% 
  filter(design == "balanced") %>% 
  group_by(ppid, ttlc_calc, cogload) %>% 
  summarise(range = max(RT) - min(RT))

head(emp_ranges)


ggplot(filter(only_responses, design == "balanced"), aes(x = ttlc_calc, y = RT, col = cogload)) +
         geom_point(alpha = .5)

range_plot <- ggplot(pred_ranges, aes(x = ttlc_calc, col = cogload, group = cogload)) +
  geom_line(aes(y = R99), alpha = .5, linetype = 2) +
    geom_line(aes(y = R95), alpha = .75, linetype = 2) +
    geom_line(aes(y = R50), alpha = 1, linetype = 2) +
  geom_line(data = emp_ranges, aes(y = range), linetype = 1) +
  geom_point(data = emp_ranges, aes(y = range)) +
  facet_wrap(~ppid) +
  scale_colour_manual(values = cols) +
  theme_classic() +
  xlab("TTLC (s)") + ylab("Ranges") + xlim(1.5,8.5) + ylim(0,7.5)

print(range_plot)

  
```


```{r, lane position over time smoothed plot}

#smoothed plot with bounds. 


```

```{r, metrics of steering quality, descriptive plotting}

```



```{r, old useful code, eval = FALSE}


nl_bf_sig2 <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload)),  sigma ~ 1 + ttlc_calc + cogload,
            b1 ~1, b2 ~ 1, nl = TRUE)

prior2 = c(prior(normal(0, 4), nlpar = "b1"),
    prior(normal(0, 4), nlpar = "b2"))

nl1_sig2 = brm(data = only_responses, formula = nl_bf_sig2, prior = prior2, family = gaussian())

summary(nl1_sig2)
loo(nl1_sig2, nl1_sig)
loo_model_weights(nl1_sig2, nl1_sig)
pp_check(nl1_sig2)

nl_bf_sig3 <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload)),  sigma ~  0 + ttlc_calc + cogload + (1 | ppid),
            b1 ~1, b2 ~ 1, nl = TRUE)

prior2 = c(prior(normal(0, 4), nlpar = "b1"),
    prior(normal(0, 4), nlpar = "b2"))

nl1_sig3 = brm(data = only_responses, formula = nl_bf_sig3, prior = prior2, family = gaussian(),
               iter = 5000, cores = 4, refresh = 500, chains = 4, warmup = 1000, control = list(adapt_delta = 0.90))

summary(nl1_sig3)
loo(nl1_sig3, nl1_sig2, nl1_sig)
loo_model_weights(nl1_sig3, nl1_sig2, nl1_sig)
pp_check(nl1_sig3)

nl_bf_sig4 <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload) + (b3*ttlc_calc*cogload)),  sigma ~  0 + ttlc_calc + cogload + (1 | ppid),
            b1 ~1, b2 ~ 1, b3 ~ 1, nl = TRUE)

prior3 = c(prior(normal(0, 3), nlpar = "b1"),
    prior(normal(0, 3), nlpar = "b2"),
    prior(normal(0, 3), nlpar = "b3"))

nl1_sig4 = brm(data = only_responses, formula = nl_bf_sig4, prior = prior3, family = gaussian(),
               iter = 5000, cores = 4, refresh = 500, chains = 4, warmup = 1000, control = list(adapt_delta = 0.90))

#improvement.
summary(nl1_sig4)
loo(nl1_sig4, nl1_sig3, nl1_sig2, nl1_sig)
loo_model_weights(nl1_sig4, nl1_sig3, nl1_sig2, nl1_sig)
pp_check(nl1_sig4)

nl_bf_sig4.1 <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload) + (b3*ttlc_calc*cogload)),  sigma ~  1 + ttlc_calc + cogload + (1 | ppid),
            b1 ~1, b2 ~ 1, b3 ~ 1, nl = TRUE)

nl1_sig4.1 = brm(data = only_responses, formula = nl_bf_sig4.1, prior = prior3, family = gaussian(),
               iter = 5000, cores = 4, refresh = 500, chains = 4, warmup = 1000, control = list(adapt_delta = 0.90))

#should sigma have an intercept? LOO says that the intercept 4.1 is worse than the non-intercept 4
summary(nl1_sig4.1)
pp_check(nl1_sig4.1)
loo(nl1_sig4, nl1_sig4.1)


nl_bf_sig5 <- bf(log_RT ~ log((b1 * ttlc_calc) + (b2 * cogload) + (b3*ttlc_calc*cogload)),  sigma ~  0 + ttlc_calc + cogload + (1 | ppid),
            b1 ~ 1 + (1 | ppid), b2 ~ 1 + (1 | ppid), b3 ~ 1 + (1 | ppid), nl = TRUE)

prior3 = c(prior(normal(0, 3), nlpar = "b1"),
    prior(normal(0, 3), nlpar = "b2"),
    prior(normal(0, 3), nlpar = "b3"))

nl1_sig5 = brm(data = only_responses, formula = nl_bf_sig5, prior = prior3, family = gaussian(),
               iter = 10000, cores = 4, refresh = 500, chains = 1, warmup = 1000, control = list(adapt_delta = 0.99))

summary(nl1_sig5)
loo(nl1_sig5, nl1_sig4)
loo_model_weights(nl1_sig5, nl1_sig4, nl1_sig3, nl1_sig2, nl1_sig)
pp_check(nl1_sig5)
plot_ribbon(nl1_sig5, only_responses, 'nl5_ribbon.png', 'ttlc_calc','RT')
plot_hist(nl1_sig5, only_responses, 'nl5_hist.png', 'RT', 'time_remaining')
save(nl1_sig5, file ='nl5.rda')

nl_bf_sig5.trunc <- bf(log_RT | trunc(ub = log_TR) ~ log((b1 * ttlc_calc) + (b2 * cogload) + (b3*ttlc_calc*cogload)),  sigma ~  0 + ttlc_calc + cogload + (1 | ppid),
            b1 ~ 1 + (1 | ppid), b2 ~ 1 + (1 | ppid), b3 ~ 1 + (1 | ppid), nl = TRUE)

nl1_sig5.trunc = brm(data = only_responses, formula = nl_bf_sig5.trunc, prior = prior3, family = gaussian(),
               iter = 10000, cores = 4, refresh = 500, chains = 1, warmup = 1000, control = list(adapt_delta = 0.99))
#mu_identity, sigma_log

summary(nl1_sig5.trunc)

save(nl1_sig5.trunc, file ='nl5_trunc.rda')

```

