---
title: 'Silent Failures in Automation RERUN. 20 participants. Pre-reg: https://osf.io/mydfw'
author: "Callum Mole"
output:
  html_document:
    df_print: paged
  html_notebook:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
---

## Introduction

I report on 20 participants who participated in our Silent Failures paradigm. Half the experiment was factorial: two cognitive loads (NoLoad, Load) and four factored failure severities (_Steering Angle Bias_; SAB). In the other half of the experiment the failure severities and onset times were quasi-random so that there was a spread of different types. The pre-registration can be found at https://osf.io/mydfw. The primary hypothesis is the effect of cognitive load on reaction times. 


```{r Load preliminaries, include=FALSE, warning=FALSE}

library("tidyverse")
library(magrittr) #for extra pipe functions
library(cowplot)
library("wesanderson")
library(brms)
library(tidybayes)

#theme for plots on TRANSITION grant.
theme_transition_report <- theme_classic() +
  theme(strip.background = element_rect(fill=NA,color=NA), 
        strip.text = element_text(face="bold",colour="black",size="12"), 
        axis.title = element_text(face="bold",colour="black",size="12"),
        axis.text.x = element_text(vjust=-.5),
        axis.text.y = element_text(vjust=.5),
        axis.text = element_text(face="plain",colour="black",size="10"),
        legend.text = element_text(face="plain",colour="black",size="10"),
        legend.title = element_text(face="bold",colour="black",size="12"),
        legend.key = element_blank()
        #panel.grid.major.y = element_line(color="grey85",size=.2, linetype = 2)
        )

```


```{r Load data, echo=FALSE, message=FALSE, warning=FALSE}

#set working directory to folder that hosts the binary files.
setwd("C:/git_repos/Orca18_Analysis/Post-Processing/")

#load steergaze data


#steergazedata <- read_csv("../Data/Orca19_collated_steering.csv")  
#saveRDS(steergazedata, "../Data/Orca19_collated_steering.rds")
steergazedata <- readRDS("../Data/Orca19_collated_steering.rds")  


steergazedata <- steergazedata %>% 
rename(swv = swa) %>% 
mutate(swa = swv * 90)

#mirror data
steergazedata <- steergazedata %>% 
mutate(world_x_mirrored = if_else(bend == -1, world_x * -1, world_x),
       swa_mirrored = if_else(bend == -1, swa * -1, swa),
       swv_mirrored = if_else(bend == -1, swv * -1, swv),
       sb_mirrored = if_else(bend == -1, steeringbias * -1, steeringbias))


#unsophisticated calculation of TTC using rate of change in steering bias
calc_TTC <- function(sb_mirrored, sb_change){

  #need to incorporate the proximity to road edges and direction of travel.
  
  sb_mirrored <- array(sb_mirrored) #needs to be an array to use apply
  
  road_edges <- c(-1.5, 1.5)
  
  distance_to_edges <- apply(sb_mirrored, 1, function(x) road_edges - x)
  
  TTLCs <- apply(distance_to_edges,1, function(x) x / (sb_change * 60))
  
  TTLC <- apply(TTLCs, 1, max)
  
  return(TTLC)
    
}
  
#add ttlc
steergazedata <- steergazedata %>% 
mutate(sb_change = prepend(diff(sb_mirrored), NA),
       TTLC = calc_TTC(sb_mirrored, sb_change)
       )


  #add RT and disengage flag.
disengage_RT <- function(onsettime, timestamp_trial, autoflag){

  #pick first frame where autoflag == false, then take the timestamp and minus the onset_time
  auto_false <- which(autoflag == "FALSE")
  disengage_index <- first(auto_false)
  disengage_trialtime <- timestamp_trial[disengage_index]
  onset_time <- first(onsettime)
  RT <- disengage_trialtime - onset_time #can be negative
  return(RT)
  
}

#calculate RT
steergazedata <- steergazedata  %>% 
group_by(ppid, sab, cogload, trialn) %>% 
mutate(RT = disengage_RT(onsettime, timestamp_trial, autoflag),
      disengaged = ifelse(is.na(RT), 0, 1) #whether or not they actually took over.
      )

#create unique trial id
steergazedata <- steergazedata %>% 
  mutate(trialid = paste(ppid, cogload, trialn, sep = "_"))

steergazedata$cogload <- as.factor(steergazedata$cogload)


#rename cogload factors so that it ameks sense
steergazedata$cogload<- plyr::mapvalues(steergazedata$cogload, from = c("None", "Middle"), to = c("noload", "load"))

balanced_steerdata <- steergazedata %>% 
  filter(design=="balanced")

random_steerdata <- steergazedata %>% 
  filter(design=="random")

#refactor sab for 
balanced_steerdata <- balanced_steerdata %>% 
ungroup() %>% 
mutate (failure_type = case_when( sab == -0.3039716 ~ ".3",
                                  sab == -0.52191351 ~ ".5",
                                  sab == -1.19868047 ~ "1.19",
                                  sab == -5.72957795 ~ "5.72"
                                  )
        ) %>% 
mutate(failure_type = as.factor(failure_type),
       cogload = as.factor(cogload),
       ppid = as.factor(ppid))



#we now have two data frames. "balanced_steerdata" and "random_steerdata"



```


```{r data logging, echo=FALSE, message=FALSE, warning=FALSE, include = FALSE, fig.width=10.5,fig.height=4.5,fig.cap="Fig 1. Amount of trials in each condition"}

#count the trials.

#Each participant experiences 4 (SAB) x 6 (repetitions) + 24 (sobel/random trials) = 48 x 2 (cognitive load) 

pp1_trials <- steergazedata %>% 
  filter(ppid == 1) %>% 
  ungroup() %$% 
  unique(trialid)


pp2_trials <- steergazedata %>% 
  filter(ppid == 2) %>% 
  ungroup() %$% 
  unique(trialid)
  

```
We deal first with the _Balanced_ dataset, since these data were designed to test our primary hypotheses. First we check how many participants took over prematurely or who did not disengage. You can see from the tables below that participants took over before the failure in a minute amount of trials, and disengaged on every failure in the balanced trials (even though for the least severe failure the vehicle technically doesn't leave the road). In the _Random_ dataset (which has more gradual failures) there are less takeovers, and more of these takeovers are premature. 


```{r calculate RT takeover measure, echo=FALSE, message=FALSE, warning=FALSE}


#RT and disengaged are already calculated.
steergaze_trialavgs <- steergazedata  %>% 
  ungroup() %>% 
  group_by(ppid, cogload, trialn) %>% 
  summarize(RT = first(RT),
            disengaged = first(disengaged), #whether or not they actually took over.
            premature = ifelse(RT <= 0, 1, 0),
            sab = first(sab),
            onsettime = first(onsettime),
            design = first(design))



#disengage %
disengage_perc <- steergaze_trialavgs %>% 
  ungroup() %>% 
  summarise(pc = sum(disengaged) / n()) 

disengage_bygroups <- steergaze_trialavgs %>% 
  ungroup() %>%
  filter(design == "balanced") %>% 
  group_by(sab, cogload) %>% 
  summarise(pc_disengaged = sum(disengaged) / n()) 

knitr::kable(disengage_bygroups)

  #negative RT %
premature_perc <- steergaze_trialavgs %>% 
  ungroup() %>% 
  summarise(pc = sum(na.omit(premature)) / n()) 

premature_bygroups <- steergaze_trialavgs %>% 
  ungroup() %>% 
  filter(design == "balanced") %>% 
  group_by(sab, cogload) %>% 
  summarise(pc_premature = sum(na.omit(premature)) / n()) 

knitr::kable(premature_bygroups)
  

```

Fig 1 below graphs the distribution of takeovers for each failure type (pooled over cognitive load). There is an intriguing double bump in each distribution.

```{r plotting RT takeover, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10.5,fig.height=4.5,fig.cap="Fig 1. RT takeover across balanced failure types"}

#first plot is the RTs across different failure types. Boxplots or density estimates are good option.

ggplot(filter(steergaze_trialavgs, design == "balanced"), aes(x = RT, group = factor(sab), fill = factor(sab))) +
  geom_density(alpha = .8) +
  xlim(c(0,10)) +
  scale_fill_manual(values = rev(wes_palette("BottleRocket2",n=4)), name = "Failure TTLC (s)", labels = c("2.23", "4.68", "7.1", "9.5")) +
  theme_transition_report +
  xlab(expression("RT"["takeover"]*" (s)"))

```

Fig 2 below splits these distributions according to cognitive load. The distributions for the Loaded conditions are wider.

```{r plotting RT takeover within failure type conditions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14,fig.height=4.5,fig.cap="Fig 2. RT takeover across cognitive loads for balanced conditions"}

#first plot is the RTs across different failure types. Boxplots or density estimates are good option.
cols = wes_palette("Darjeeling1", n=2)

head(steergaze_trialavgs)
p_load <- ggplot(filter(steergaze_trialavgs, design == "balanced",cogload=="load"), aes(x = RT, group = factor(sab))) +
  geom_density(alpha = .8, aes(fill = cols[1])) +
  xlim(c(0,10)) +
  theme_transition_report +
  xlab(expression("RT"["takeover"]*" (s)"))

p_cogload <- p_load +
  geom_density(data = filter(steergaze_trialavgs, design == "balanced", cogload == "noload"),
                 aes(x = RT, group = factor(sab), fill = cols[2]),
                 alpha = .5) +
    scale_fill_identity(name = 'Cognitive Load',
  labels = c('Load','NoLoad'), breaks = c(cols[1],cols[2]), 
  guide = 'legend') 


show(p_cogload)

```


```{r plotting swa, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15,fig.height=8,fig.cap="Fig 9. swa for cogload within different failure types. The dashed line is the point of takeover"}


#pick up .5 s before trial takeover so you can see how quickly swa moves after takeover.

delay = 1
steergaze_manual_delay <- steergazedata %>% 
  ungroup() %>% 
  group_by(trialid) %>% 
  filter(timestamp_trial > (RT + onsettime - delay))

### Reset trial so they all start at around [0,0] 
steergaze_manual_delay <- steergaze_manual_delay %>% 
  ungroup() %>% 
  group_by(trialid) %>%
  mutate(timestamp_zero = timestamp_trial - timestamp_trial[1],
         f = seq(1:n()))


#plot steering bias
p_swa <- ggplot(data = filter(steergaze_manual_delay, f < 360), aes(x = timestamp_zero - delay, y= swa_mirrored)) +
  geom_path(aes(group = trialid), alpha = .1) +
  theme_transition_report +
  ylim(c(-45,90)) +
  xlab("Time (s)") + ylab("Steering Wheel Angle (degrees)") +
  geom_vline(xintercept = 0, col = "black", linetype = "dashed")
  
show(p_swa)


```



```{r plot TTLC, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15,fig.height=6,fig.cap="Fig 11. A) Lane position and RT takeover. B) TTLC and RT takever"}

#what do I want to plot? 

#TTLC @ takeover next to RT?
#add delay? 
takeover_state<- steergazedata %>%
  ungroup() %>% 
  filter(autoflag == FALSE) %>% 
  group_by(trialid) %>%
  summarise(x = first(world_x_mirrored),
            z = first(world_z),
            sb = first(steeringbias),
            sb_mirrored = first(sb_mirrored),
            sb_change = first(sb_change),
            cogload = first(cogload),
            sab = first(sab),
            onset = first(onsettime),
            time = first(timestamp_trial),
            RT = first(RT),
            TTLC = first(TTLC),
            simulated_ttlc = first(simulated_ttlc),
            bend = first(bend),
            ppid = first(ppid),
            swa_max = max(swa_mirrored, na.rm = T),
            autofile = first(autofile),
            design = first(design))


p_sb_RT <- ggplot(data = filter(takeover_state, TTLC < 10, RT > 0, sab < 0), aes(x = sb_mirrored, y=RT, col = factor(design))) + 
  geom_point(alpha = .4) +
  theme_transition_report +
  xlab(expression("Lane Position (m)")) + ylab(expression("RT"["takeover"]*" (s)")) 


p_sb_ttlc <- ggplot(data = filter(takeover_state, TTLC < 10, RT > 0, sab < 0), aes(x = TTLC, y=RT, col= factor(design))) + 
  geom_point(alpha = .4) +
  theme_transition_report +
  xlab(expression("TTLC (s)")) + ylab(expression("RT"["takeover"]*" (s)")) 
  
legend <- get_legend(p_sb_RT)
p <- plot_grid(p_sb_RT + theme(legend.position="none"),
               p_sb_ttlc + theme(legend.position="none"),
               labels = c("A", "B"), nrow=1)
p_legend <- plot_grid(p, legend, rel_widths = c(4,.5))
show(p_legend)


``` 



```{r plot SWA max and RT takeover, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15,fig.height=6,fig.cap="Fig 12. A) SWA max by RT and Failure type. B) SWA max by TTLC and Failure Type"}





#plot RT and SWA_max to compare different RTs and steering demand across Failure Type.

#This is a useful plot for understanding that steering corrections are not linked just to the speed of response.

p_swamax_RT <- ggplot(data = filter(takeover_state, RT>0, sab < 0), aes(x = RT, y = swa_max, col = factor(design))) +
  geom_point(alpha = .8) +
  #facet_wrap(~failure_type) +
  scale_colour_manual(values = rev(wes_palette("BottleRocket2",n=3)), name = "Failure Type")  +
  theme_transition_report +
  xlab(expression("RT"["takeover"]*" (s)")) + ylab(expression("swa"["max"]*" ("*degree*")")) +
  expand_limits(x = c(0, 2), y = c(15, 90))

p_swamax_sb <- ggplot(data = filter(takeover_state, RT>0, TTLC< 10, sab < 0), aes(x = sb_mirrored, y = swa_max, col = factor(design))) +
  geom_point(alpha = .8) +
  #facet_wrap(~failure_type) +
  scale_colour_manual(values = rev(wes_palette("BottleRocket2",n=3)), name = "Failure Type")  +
  theme_transition_report +
  xlab(expression("Lane Position (m)")) + ylab(expression("SWA"["max"]*" ("*degree*")")) +
  expand_limits(y = c(15, 90))

p_swamax_ttlc <- ggplot(data = filter(takeover_state, RT>0, TTLC< 10, sab < 0), aes(x = TTLC, y = swa_max, col = factor(design))) +
  geom_point(alpha = .8) +
  #facet_wrap(~failure_type) +
  scale_colour_manual(values = rev(wes_palette("BottleRocket2",n=3)), name = "Failure Type")  +
  theme_transition_report +
  xlab(expression("TTLC (s)")) + ylab(expression("SWA"["max"]*" ("*degree*")")) +
  expand_limits(x = c(0, 2), y = c(15, 90))

legend <- get_legend(p_swamax_RT)
p <- plot_grid(p_swamax_RT + theme(legend.position="none"),
               p_swamax_sb + theme(legend.position="none"),
               p_swamax_ttlc + theme(legend.position="none"),
            labels = c("A", "B", "C"), nrow=1)
p_legend <- plot_grid(p, legend, rel_widths = c(4,.5))
show(p_legend)


```


```{r calculate delayed state, echo=FALSE, message=FALSE, warning=FALSE}

delay = .25
takeover_state_delayed <- steergazedata %>%
  ungroup() %>% 
  group_by(trialid) %>% 
  filter(timestamp_trial > (RT + onsettime - delay)) %>% 
  summarise(x = first(world_x_mirrored),
            z = first(World_z),
            rads = first(radii),
            sb = first(steeringbias),
            sb_mirrored = first(sb_mirrored),
            sb_change = first(sb_change),
            cogload = first(cogload),
            failure_type = first(failure_type),
            onset = first(onsettime),
            time = first(timestamp_trial),
            RT = first(RT),
            TTLC = first(TTLC),
            bend = first(bend),
            ppid = first(ppid),
            swa_max = max(swa_mirrored, na.rm = T),
            autofile = first(AutoFile),)


```

```{r create trial history, echo=FALSE, message=FALSE, warning=FALSE}

#group by trial id and start the first exp_timestamp.
#then order by exp_timestamp.
#then trim the last, add an NA to the front.
#add it in to trial averages.
ts_exps <- steergazedata %>%
  ungroup() %>% 
  filter(autoflag == FALSE) %>% 
  group_by(ppid, trialid) %>%
  summarise(ts_exp = first(timestamp_exp),
            cogload = first(cogload),
            failure_type = first(failure_type),
            onset = first(onsettime),
            rads = first(radii),
            RT = first(RT),
            TTLC = first(TTLC),
            swa_max = max(swa_mirrored, na.rm = T))

shiftvector <- function(x){
  
  #shift vector forward one.
  x = prepend(x,NA)
  x = x[-length(x)]
  
}

ts_exps <- ts_exps %>% 
  group_by(ppid) %>% 
  arrange(ts_exp) %>% 
  mutate(cogload_hist = shiftvector(cogload),
         failure_type_hist = shiftvector(failure_type),
         onset_hist = shiftvector(onset),
         rads_hist = shiftvector(rads))
  
ts_exps <- ts_exps %>%
  arrange(ppid)

levels(ts_exps$failure_type)
levels(ts_exps$cogload)

#1 = Sudden, 2 = Gradual, 3 = Benign
#1 = Easy, 2 = Hard, 3 = None.

ggplot(data = filter(ts_exps, TTLC < 10, RT >0), aes(x = RT, group = factor(failure_type_hist), col = factor(failure_type_hist))) + 
  geom_density(alpha = .8) +
  facet_wrap(~failure_type, scales = "free") +
  scale_colour_manual(values = rev(wes_palette("BottleRocket2",n=3)), name = "Failure Type History")  +
  theme_transition_report


```


```{r basic regression modelling of RT, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}


#ggplot(takeover_state_delayed, aes(x = RT)) + geom_density()
#only model failure types with a 100% takeover rate.
data <- takeover_state_delayed %>% 
  filter(failure_type != "Benign", RT > 0)

#scale your variables by centering then dividing by two standard deviations http://www.stat.columbia.edu/~gelman/research/unpublished/standardizing.pdf
data <- data %>% 
  mutate(sb_mirrored.z = (sb_mirrored - mean(sb_mirrored)) / (2 * sd(sb_mirrored)),
         sb_change.z = (sb_change - mean(sb_change)) / (2 * sd(sb_change)),
         TTLC.z = (TTLC - mean(TTLC) / (2 * sd(TTLC))))

cor(data$sb_mirrored.z, data$sb_change.z)
cor(data$sb_mirrored.z, data$RT)
cor(data$RT, data$sb_change.z)

#ggplot(data, aes(x = RT)) + geom_density()

m_rt_gauss = brm(RT ~ sb_mirrored.z * sb_change.z, data = data,
            family = gaussian(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)
save(m_rt, file ="m_rt.rda")

m_rt_logn = brm(RT ~ sb_mirrored.z * sb_change.z, data = data,
            family = lognormal(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)


m_rt_weib = brm(RT ~ sb_mirrored.z * sb_change.z, data = data,
            family = weibull(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

print(m_rt_gauss)
pp_check(m_rt_gauss) #doesn't seem to capture either of the peaks very well. 
pp_check(m_rt_logn)
pp_check(m_rt_weib)

loo(m_rt_gauss, m_rt_logn, m_rt_weib)
loo_model_weights(m_rt_gauss, m_rt_logn, m_rt_weib)

#gauss clearly better.

m_rt_gauss_ppid = brm(RT ~ sb_mirrored.z * sb_change.z + (1 | ppid), data = data,
            family = gaussian(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)
  
loo(m_rt_gauss, m_rt_gauss_ppid)
loo_model_weights(m_rt_gauss, m_rt_gauss_ppid)
pp_check(m_rt_gauss_ppid)
#non hierarchical appears to be better.

#plot model output.
plot(m_rt_gauss)
plot(marginal_effects(m_rt_gauss, effects = "sb_mirrored.z:sb_change.z"))
plot(marginal_effects(m_rt_gauss, effects = "sb_mirrored.z"))
plot(marginal_effects(m_rt_gauss, effects = "sb_change.z"))

#let's plot it against the raw data. 
fitted_RT_estimates <- as.data.frame(fitted(m_rt_gauss, re_formula = NA))

#plot against actual data. 

data$predicted <- fitted_RT_estimates$Estimate
ggplot(data = data, aes(x = RT)) + geom_density(col = "black") +
  geom_density(data = fitted_RT_estimates, aes(x = Estimate), col = "blue")

ggplot(data = data, aes(x = RT, y = predicted)) + geom_point() +
  geom_abline(slope=1)

print(m_rt_gauss)


m_rt_sb <- brm(RT ~ sb_mirrored.z, data = data,
            family = gaussian(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

pp_check(m_rt_sb)

m_rt_sb_ch <- brm(RT ~ sb_mirrored.z + sb_change.z, data = data,
            family = gaussian(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)

pp_check(m_rt_sb_ch)

pp_check(m_rt_gauss)

loo(m_rt_sb, m_rt_sb_ch, m_rt_gauss)
loo_model_weights(m_rt_sb, m_rt_sb_ch, m_rt_gauss)

#let's fit the same model for benign failures as well. 

#all failures definitely do not work. Takeover in non-critical failures needs to be modelled differently. 
data_allfailures <- takeover_state_delayed %>% 
  filter(RT > 0, sb_mirrored < 0)

data_allfailures <- data_allfailures %>% 
  mutate(sb_mirrored.z = (sb_mirrored - mean(sb_mirrored)) / (2 * sd(sb_mirrored)),
         sb_change.z = (sb_change - mean(sb_change)) / (2 * sd(sb_change)))

m_rt_allfailures = brm(RT ~ sb_mirrored.z * sb_change.z, data = data_allfailures,
            family = gaussian(),
            iter = 3000, cores = 4, refresh = 500, chains = 1, warmup = 1000)
print(m_rt_allfailures)
plot(marginal_effects(m_rt_allfailures, effects = "sb_mirrored.z:sb_change.z"))
pp_check(m_rt_allfailures)



```

<!---
 
Therefore, we recommend massively increasing the levels (e.g. ten levels) of silent failures so we have a decent breadth of SABs (and therefore TTCs) to fit models to. Only using one radii will increase the amount of levels we can assess. To ensure even coverage we will keep the design factorial, this means we can also do inferences on the data between conditions.

Jami has also suggested that we could look model cognitive load as reducing sampling rate. Worth pursuing and I think would mean keeping the cognitive load conditions... 

Another design change is increasing sensitivity of the steering wheel to lift the capping confound of the wheel angles...

-->

<!-- 
After discussing with Richard we decided that some regression analysis was needed with first, second and third order perceptual variables to see what combination of measures best predicts RT.

Another measure in there could be the trial type at n-1. For example, if there was a sudden trial preceding a benign trial, it is probably more likely that they would take over earlier than usual in the benign trial. To examine this you want to striate the TTLC by RT plot with N-1 failure_type.

A useful plot might be TTLC and/or Steering Bias by Steering magnitude.

31/05. Jami Discussion about the importance of orientation as well as the lane position. We concluded that this is captured within sb_change. And that lane position and sb_change should be inputted to the multiple regression independently of TTLC, because the TTLC assumes a particular relationship within the calculation. 

-->

### Other Pre-registered Hypotheses
 

In the pre-registration there were three more hypotheses. Here I briefly list what we now know.
 
- __H3__: Participants will sample from a more constricted region of the screen for increased cognitive load.

_Not looked at yet, will look at if I have time before hols, but do not clearly see how this will change the design?_

- __H4__: These effects of cognitive load will increase as cognitive load difficulty increases.

_For sudden failures RT~takeover~ appears to be stratified somewhat by Easy or Hard load. However, this effect is small, and smaller still (or nonexistent) in the less severe failures_.

- __H5__: Effects of cognitive load will become more pronounced when the (steering) task is more difficult (for sharp bends and sudden silent failures). 

_There does not seem to be an interaction jumping out for bend radii. As stated above the small effects of cognitive load are more pronounced for silent failures_. 
 
<!-- 

One might predict that ttlc does not vary since this is a candidate for the threshold one is responding to. 


issue of capped steering wheel angles at large angles produces inability to correct quick enough for sudden failures. 

-->



<!-- 
Gaze with and without cognitive load.
Gaze with and without automation. 
-->

