---
title: 'Silent Failures in Automation RERUN. 20 participants. Pre-reg: https://osf.io/mydfw'
author: "Callum Mole"
output:
  html_document:
    df_print: paged
  html_notebook:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
---

## Introduction

I report on 20 participants who participated in our Silent Failures paradigm. Half the experiment was factorial: two cognitive loads (NoLoad, Load) and four factored failure severities (_Steering Angle Bias_; SAB). In the other half of the experiment the failure severities and onset times were quasi-random so that there was a spread of different types. The pre-registration can be found at https://osf.io/mydfw. The primary hypothesis is the effect of cognitive load on reaction times. 


```{r Load preliminaries, include=FALSE, warning=FALSE}

library("tidyverse")
library(magrittr) #for extra pipe functions
library(cowplot)
library("wesanderson")
library(brms)
library(tidybayes)

#theme for plots on TRANSITION grant.
theme_transition_report <- theme_classic() +
  theme(strip.background = element_rect(fill=NA,color=NA), 
        strip.text = element_text(face="bold",colour="black",size="12"), 
        axis.title = element_text(face="bold",colour="black",size="12"),
        axis.text.x = element_text(vjust=-.5),
        axis.text.y = element_text(vjust=.5),
        axis.text = element_text(face="plain",colour="black",size="10"),
        legend.text = element_text(face="plain",colour="black",size="10"),
        legend.title = element_text(face="bold",colour="black",size="12"),
        legend.key = element_blank()
        #panel.grid.major.y = element_line(color="grey85",size=.2, linetype = 2)
        )

```


```{r Load data, echo=FALSE, message=FALSE, warning=FALSE}

#set working directory to folder that hosts the binary files.
setwd("C:/git_repos/Orca18_Analysis/Post-Processing/")

#load steergaze data


#steergazedata <- read_csv("../Data/Orca19_collated_steering.csv")  
#saveRDS(steergazedata, "../Data/Orca19_collated_steering.rds")
steergazedata <- readRDS("../Data/Orca19_collated_steering.rds")  


steergazedata <- steergazedata %>% 
rename(swv = swa) %>% 
mutate(swa = swv * 90)

#mirror data
steergazedata <- steergazedata %>% 
mutate(world_x_mirrored = world_x * bend,
       swa_mirrored = swa * bend,
       swv_mirrored = swv * bend,
       sb_mirrored = steeringbias * bend)

  
#add ttlc
ttlc_from_offset <- function(b, w = 1.5, r = 60, v = 8){
  b = b / 180 * pi
  
  ttlc = sqrt(w*(2*r + sign(b)*w)/(abs(b)*r*v))
}

steergazedata <- steergazedata %>% 
mutate(sb_change = c(NA, diff(sb_mirrored)),
       ttlc_calc = ttlc_from_offset(sab)
       )


  #add RT and disengage flag.
disengage_RT <- function(onsettime, timestamp_trial, autoflag){

  #pick first frame where autoflag == false, then take the timestamp and minus the onset_time
  auto_false <- which(autoflag == "FALSE")
  disengage_index <- first(auto_false)
  disengage_trialtime <- timestamp_trial[disengage_index]
  onset_time <- first(onsettime)
  RT <- disengage_trialtime - onset_time #can be negative
  return(RT)
  
}

#calculate RT
steergazedata <- steergazedata  %>% 
group_by(ppid, sab, cogload, trialn) %>% 
mutate(RT = disengage_RT(onsettime, timestamp_trial, autoflag),
      disengaged = ifelse(is.na(RT), 0, 1) #whether or not they actually took over.
      )

#create unique trial id
steergazedata <- steergazedata %>% 
  mutate(trialid = paste(ppid, cogload, trialn, sep = "_"))

steergazedata$cogload <- as.factor(steergazedata$cogload)


#rename cogload factors so that it makes sense
steergazedata$cogload<- plyr::mapvalues(steergazedata$cogload, from = c("None", "Middle"), to = c("noload", "load"))


```

```{r plotting swa, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15,fig.height=8,fig.cap="Fig 9. swa for cogload within different failure types. The dashed line is the point of takeover"}


#pick up .5 s before trial takeover so you can see how quickly swa moves after takeover.

delay = 1
steergaze_manual_delay <- steergazedata %>% 
  ungroup() %>% 
  group_by(trialid) %>% 
  filter(timestamp_trial > (RT + onsettime - delay))

### Reset trial so they all start at around [0,0] 
steergaze_manual_delay <- steergaze_manual_delay %>% 
  ungroup() %>% 
  group_by(trialid) %>%
  mutate(timestamp_zero = timestamp_trial - timestamp_trial[1],
         f = seq(1:n()))

#plot steering bias
p_swa <- ggplot(data = filter(steergaze_manual_delay, f < 360), aes(x = timestamp_zero - delay, y= swa_mirrored)) +
  geom_path(aes(group = trialid), alpha = .1) +
  theme_transition_report +
  ylim(c(-45,90)) +
  xlab("Time (s)") + ylab("Steering Wheel Angle (degrees)") +
  geom_vline(xintercept = 0, col = "black", linetype = "dashed")
  
show(p_swa)

#plot steering bias
p_sb <- ggplot(data = filter(steergaze_manual_delay, f < 360), aes(x = timestamp_zero - delay, y= sb_mirrored)) +
  geom_path(aes(group = trialid), alpha = .1) +
  theme_transition_report +
  ylim(c(-2,2)) +
  xlab("Time (s)") + ylab("Steering Bias") +
  geom_vline(xintercept = 0, col = "black", linetype = "dashed")
  
show(p_sb)


```

```{r fitting harmonic oscillator, echo=FALSE, message=FALSE, warning=FALSE}


data_fromtakeover <- steergazedata %>% 
  ungroup() %>% 
  group_by(trialid) %>% 
  filter(timestamp_trial > (RT + onsettime)) %>% 
  mutate(timestamp_zero = timestamp_trial - timestamp_trial[1],
         f = seq(1:n()))

write.csv(data_fromtakeover, "Orca19_datafromtakeover.csv")



```





