---
title: "Looking at Cognitive Load performance"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


```{r, echo=TRUE, message=FALSE}

library("tidyverse") 

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

FilePath <- "../Data/" 
text_multiplier <- ggplot2:::.pt
ansize = 6/text_multiplier

```

```{r, wit df}

wit_pattern = "Orca19_.+\\d*_\\d*_WithinTrial.csv"
wit_files <- list.files(path = FilePath, pattern = wit_pattern, recursive = TRUE)

wit_files <- grep("pilot", wit_files, ignore.case = TRUE, invert = TRUE, value = TRUE)
wit_files <- grep("prac", wit_files, ignore.case = TRUE, invert = TRUE, value = TRUE)

wit_df = data.frame()

for (file in wit_files){
  
  newdata = read.csv(paste0(FilePath,file))
  current_ppid <- as.integer(substr(strsplit(file, "/")[[1]][1], start = 2, stop = 10))
  
  if (grepl("Middle", file)){
    block = 3 
    newdata$ppid = current_ppid #bug and all ppids of this file are set to 1
  } else {
    splt <- strsplit(file, "_")
    block = as.integer(splt[[1]][5])
  }  
  
  newdata$block = block
  
  #pp 3 has a different number of columns  
  if (first(newdata$ppid)==3){
    newdata$timestamp_exp <- NaN
    newdata$item_delay <- NaN
    newdata$currentaudio_type <- NaN
  }
  
  if (length(wit_df) == 0){
      wit_df <- newdata
  } else{
      wit_df <- rbind(wit_df, newdata) #add to existing datframe 
  }  
  
}

head(wit_df)
```

```{r, eot df}

eot_pattern = "Orca19_.+\\d*_\\d*_EndofTrial.csv"
eot_files <- list.files(path = FilePath, pattern = eot_pattern, recursive = TRUE)

eot_files <- grep("pilot", eot_files, ignore.case = TRUE, invert = TRUE, value = TRUE)
eot_files <- grep("prac", eot_files, ignore.case = TRUE, invert = TRUE, value = TRUE)

print(eot_files)

eot_df = data.frame()

for (file in eot_files){
  
  newdata = read.csv(paste0(FilePath,file))
  current_ppid <- as.integer(substr(strsplit(file, "/")[[1]][1], start = 2, stop = 10))
  
  if (grepl("Middle", file)){
    block = 3 
    newdata$ppid = current_ppid #bug and all ppids of this file are set to 1
  } else {
    splt <- strsplit(file, "_")
    block = as.integer(splt[[1]][5])
  }  
  
  newdata$block = block
  
  if (length(wit_df) == 0){
      eot_df <- newdata
  } else{
      eot_df <- rbind(eot_df, newdata) #add to existing datframe 
  }  
  
}

head(eot_df)
```


The experiment design allows many ways to capture performance. There are three obvious ways of measures performance: the speed of response, whether the participant responded appropriately, and how far off they were in their recorded target counts.

From the __wit_df__ dataframe the following measures need to be calculated:   
1. MeanRT_TruePos (MeanRT for True Positives)   
2. StdRT_TruePos (Standard deviation of RT for True Positives)   
3. Perc_Correct (True Positives and True Negatives)   

First, we want to remove any RTs that are unfeasibly quick, since they are probably responding to the previously head stimuli. Based on Luce (1986), this value is set at 100ms.

```{r}

wit_df <- wit_df %>% 
  mutate(trialid = paste(ppid, "Middle", trialn, sep = "_"))

wit_filtered <- filter(wit_df, RT == -1 | RT >.1) # Returns dataframe for rows where RT was >.1 or -1 (no response) 
```


```{r}
  
wit_tp <- filter(wit_filtered, ResponseCategory == 1) #create new dataframe only including true positives
  
SummaryRTs <- wit_tp %>% group_by(ppid, block, trialn) %>% summarise(
  targetnumber = first(targetnumber),
  targetoccurence = first(targetoccurence),
  meanRT = mean(RT),
  stdRT = sd(RT))

head(SummaryRTs) #view start of dataframe. For every participant and trial there will be a meanRT and a stdRT. stdRT is sometimes NA when there is only one True Positive for that trial. The trial will be missing if there are no True Positives for that trial. 

```

All the response categories are needed for calculating Perc_Correct, not just the True Positives.

```{r}

#Calculate the amount of each type of responses
SummaryCounts <- wit_filtered %>% group_by(ppid, block, trialn) %>% summarise(
  targetnumber = first(targetnumber),
  targetoccurence = first(targetoccurence),
  TruePos = sum(ResponseCategory==1),
  FalseNeg = sum(ResponseCategory==2), 
  FalsePos = sum(ResponseCategory==3),
  TrueNeg = sum(ResponseCategory==4), 
  TotalResponses=n())

#add an extra column with Perc_Correct.
SummaryCounts <- mutate(SummaryCounts, Perc_Correct = (TruePos + TrueNeg)/ TotalResponses)

```

```{r, pc correct}

#no inferences are made here as it's a distraction from the main points. Just print some useful info.


SummaryCounts %>% 
  group_by(ppid, block) %>% 
  summarise(mn_pc = mean(Perc_Correct)) %>% 
  ungroup() %>% 
  group_by(block) %>% 
  summarise(mean_pc = mean(mn_pc),
            sd_pc = sd(mn_pc))

ppid_pcs <- SummaryCounts %>% 
  filter(block == 3) %>% 
  group_by(ppid) %>% 
  summarise(mn_pc = mean(Perc_Correct))

SummaryRTs %>% 
  group_by(ppid, block) %>% 
  summarise(mn_rt = mean(meanRT, na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(block) %>% 
  summarise(mean_rt = mean(mn_rt),
            sd_rt = sd(mn_rt))

ppid_rts <- SummaryRTs %>% 
  filter(block == 3) %>% 
  group_by(ppid) %>% 
  summarise(mn_rt = mean(meanRT, na.rm = TRUE))



```


```{r, load steering measures}

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

#load steer data
steerdata <- readRDS("../Data/Orca19_collated_steering2.rds")  

steerdata$autoflag<- plyr::mapvalues(steerdata$autoflag, from = c("True", "False"), to = c("TRUE", "FALSE"))

steerdata <- steerdata %>% 
  mutate(trialid = paste(ppid, cogload, trialn, sep = "_"))

disengage_RT <- function(onsettime, timestamp_trial, autoflag){
  
  #pick first frame where autoflag == false, then take the timestamp and minus the onset_time
  auto_false <- which(autoflag == "FALSE")
  disengage_index <- first(auto_false)
  disengage_trialtime <- timestamp_trial[disengage_index]
  onset_time <- first(onsettime)
  RT <- disengage_trialtime - onset_time #can be negative
  return(RT)
  
}

steerdata <- steerdata  %>% 
  group_by(ppid, sab, cogload, trialn) %>% 
  mutate(RT = disengage_RT(onsettime, timestamp_trial, autoflag),
         disengaged = ifelse(is.na(RT), 0, 1) #whether or not they actually took over.
  )


#mirror data
steerdata <- steerdata %>% 
  mutate(sb_mirrored = if_else(bend == -1, steeringbias * -1, steeringbias))

steerdata <- filter(steerdata, cogload == "Middle")

sb_summary <- steerdata %>% 
  group_by(trialid) %>% 
  summarise(maxsb = max(abs(sb_mirrored)),
            ppid = first(ppid)) %>% 
  ungroup() %>% 
  group_by(ppid) %>% 
  summarise(mn_maxsb = mean(maxsb))

rt_summary <- steerdata %>% 
  group_by(trialid) %>% 
  summarise(RT = first(RT),
            ppid = first(ppid)) %>% 
  ungroup() %>% 
  group_by(ppid) %>% 
  summarise(mn_RT = mean(RT, na.rm = TRUE))


```

```{r, tradeoff}

#this chunk is a pretty superficial look at whether some measures of error on the cognitive task correlate with maximum steerinb bias, or RT in the steering task. 

# The correlations are weak, and it's not an integral part of the study, so I haven't investigated further.

ppid_pcs <- left_join(ppid_pcs, sb_summary, by = "ppid")
ppid_pcs <- left_join(ppid_pcs, rt_summary, by = "ppid")
ppid_rts <- left_join(ppid_rts, sb_summary, by = "ppid")
ppid_rts <- left_join(ppid_rts, rt_summary, by = "ppid")


ggplot(ppid_pcs, aes(x = mn_maxsb, y = mn_pc)) + geom_point()
ggplot(ppid_pcs, aes(x = mn_RT, y = mn_pc)) + geom_point()
ggplot(ppid_rts, aes(x = mn_maxsb, y = mn_rt)) + geom_point()
ggplot(ppid_rts, aes(x = mn_RT, y = mn_rt)) + geom_point()


cor(ppid_pcs$mn_pc, ppid_pcs$mn_maxsb)
cor(ppid_pcs$mn_pc, ppid_pcs$mn_RT)
cor(ppid_rts$mn_rt, ppid_rts$mn_maxsb)
cor(ppid_rts$mn_rt, ppid_rts$mn_RT)


```

```{r, methods fig, trial sequence, fig.height = 2, fig.width=3.5}

#library(RColorBrewer)
#cols <- brewer.pal(6, "Paired")[3:6]

mycol = "#ff7f0e"
#pick trial
trialids <- steerdata %>% 
  filter(ppid>3, cogload == "Middle", simulated_ttlc > 4.6, simulated_ttlc < 4.8) %>% 
  select(trialid) %>% 
  unique(.)

trial <- sample(trialids$trialid,1)

trial_steer <- filter(steerdata, trialid == trial)
trial_cog <- filter(wit_df, trialid == trial)
trial_cog <- trial_cog %>% 
  mutate(CurrentAudio = toupper(CurrentAudio))
targets <- filter(trial_cog, currentaudio_type == "T")
distractors <- filter(trial_cog, currentaudio_type == "D")

#head(trial_cog)

takeover_frame <-  trial_steer[first(which(trial_steer$autoflag == "FALSE")),]
onset_frame <- (filter(trial_steer, timestamp_trial > first(trial_steer$onsettime)))[1,]
first_frame <- trial_steer[1,]
time_axis <- data.frame(ts = seq.int(0, 15), ts_exp = seq.int(0,15) + first_frame$timestamp_exp)

#head(onset_frame)
#head(trial_cog)
#head(trial_steer)

t_y = .75

leg_v = .22 #vertical spacing
leg_t = -.7 #starting top
leg_l = first_frame$timestamp_exp+13 #left align
leg_h = .32 #space between dot and text
lw = .5 #width of labels
leg_t1 = -.5 #starting top
leg_l1 = first_frame$timestamp_exp+.5

p_timings <- ggplot(trial_steer, aes(x = timestamp_exp, y = sb_mirrored)) + 
  
  
  
  #labels
  #geom_text(data = onset_frame, aes( x = timestamp_exp - 1, y = sb_mirrored - .8, label = "Failure onset"), size = ansize) +
  #geom_segment(data = onset_frame, aes(x = timestamp_exp - 1, xend = timestamp_exp - .1, y = sb_mirrored -.7, yend = sb_mirrored - .1), colour = "black", size=.75, alpha=1, arrow=arrow(angle = 20, length = unit(0.1, "cm"), type = "closed")) +
  #geom_text(data = takeover_frame, aes( x = timestamp_exp - 1, y = sb_mirrored - .6, label = "Takeover"), size = ansize) +
  #geom_segment(data = takeover_frame, aes(x = timestamp_exp - 1, xend = timestamp_exp - .1, y = sb_mirrored - .5, yend = sb_mirrored - .1), colour = "black", size=.75, alpha=1, arrow=arrow(angle = 20, length = unit(0.1, "cm"), type = "closed")) +
  
  
  
  #cogtask
  geom_segment(data = targets, aes(x = timestamp_exp, xend = timestamp_exp, y = 0, yend = t_y), col = "grey40") +
  #geom_segment(data = filter(targets, ResponseCategory == 1), aes(x = timestamp_exp, xend = timestamp_exp + RT, y = t_y, yend = t_y), linetype = "dotted", col = "grey40") +
    geom_segment(data = filter(targets, ResponseCategory == 1), aes(x = timestamp_exp + RT, xend = timestamp_exp + RT, y = 0, yend = t_y), col = "green3") +
  geom_point(data = filter(targets, ResponseCategory == 1), aes(x = timestamp_exp + RT, y = t_y), fill = "green3", col = "green3", shape = 22) +

  geom_text(data = targets, aes(x = timestamp_exp, y = t_y+.15, label = CurrentAudio), size = ansize, col = "grey40") +
  geom_segment(data = distractors, aes(x = timestamp_exp, xend = timestamp_exp, y = 0, yend = .5), col = "grey60", linetype = "dotted") + 
  geom_text(data = distractors, aes(x = timestamp_exp, y = .65, label = CurrentAudio), size = ansize, col = "grey60") +
  
  #scale_color_manual(values = c("TRUE" = cols[4], "FALSE" = cols[3])) +
  scale_linetype_manual(values=c("TRUE" = "solid", "FALSE" = "dotted")) +
  guides(linetype = FALSE) +
  #guides(col = FALSE) +
  
  
  
  #time axis
  geom_line(data = time_axis, aes(x = ts_exp, y = 0)) +
  geom_point(data = time_axis[1,], aes(x = ts_exp, y = 0), size = 2) +
  geom_point(data = tail(time_axis,1), aes(x = ts_exp, y = 0), size = 2) +
  geom_text(data = tail(time_axis,1), aes(x = ts_exp, y = -.2, label = paste0(ts, " s")), size = ansize) +
  geom_text(data = head(time_axis,1), aes(x = ts_exp, y = -.2, label = paste0(ts, " s")), size = ansize) +
  geom_segment(data = time_axis, aes(x = ts_exp, y = 0, xend = ts_exp, yend = .05)) +
  
  #steering signal
  geom_path(aes(group = autoflag, linetype = autoflag), col = mycol) +
  geom_point(data = onset_frame, fill = "black", col = "black", shape = 23) +
  geom_point(data = takeover_frame, fill = "black", col = "black", shape = 23) +
  scale_y_reverse(lim = c(1.5,-1.5)) +
  theme_classic() +
  

  #custom legend
  annotate("segment", x = leg_l1-lw, xend = leg_l1, y= leg_t1, yend = leg_t1, col = "grey60", linetype = "dotted") +
  annotate("text", x = leg_l1+leg_h, y = leg_t1, label = "Distractors", hjust = 0, vjust = .5, size = ansize) +
  
  annotate("segment", x = leg_l1-lw, xend = leg_l1, y= leg_t1 - (leg_v), yend = leg_t1 - (leg_v), col = "grey40") +
  annotate("text", x = leg_l1+leg_h, y = leg_t1 - (leg_v), label = "Targets", hjust = 0, vjust = .5, size = ansize) +
  
  annotate("point", x = leg_l1-(lw/2), y= leg_t1 - (2*leg_v), fill="green3", col = "green3", shape = 22) +
  annotate("text", x = leg_l1+leg_h, y = leg_t1 - (2*leg_v), label = "Button Press", hjust = 0, vjust = .5, size = ansize) +

  #annotate("segment", x = leg_l-leg_h, xend = leg_l, y= leg_t, yend = leg_t, col = mycol) +
  #annotate("text", x = leg_l+leg_h, y = leg_t, label = "Automation", hjust = 0, vjust = .5, size = ansize) +
    
    #annotate("segment", x = leg_l-leg_h, xend = leg_l, y= leg_t - (1*leg_v), yend = leg_t - (1*leg_v), col = mycol, linetype = "dotted") +
  #annotate("text", x = leg_l+leg_h, y = leg_t - (1*leg_v), label = "Manual", hjust = 0, vjust = .5, size = ansize) +

  #remove axis 
  theme(axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank()) 
  
  
print(p_timings)
p_timings <- p_timings + scale_y_reverse(lim = c(1,-1.5)) 
print(p_timings)
ggsave("p_methods_timings.eps", plot = p_timings, dev = cairo_ps, width = 13.2, height = 5, units = "cm", dpi = 300)
ggsave("p_methods_timings.svg", plot = p_timings, width = 9, height = 5, units = "cm", dpi = 300)

```

```{r, methods without cog, trial sequence, fig.height = 4, fig.width=3.5}

#library(RColorBrewer)
#cols <- brewer.pal(6, "Paired")[3:6]

mycol = "#ff7f0e"
#pick trial
trialids <- steerdata %>% 
  filter(ppid>3, cogload == "Middle", simulated_ttlc >4.6, simulated_ttlc < 4.8) %>% 
  select(trialid) %>% 
  unique(.)

trial <- sample(trialids$trialid,1)

trial_steer <- filter(steerdata, trialid == trial)

head(trial_cog)

takeover_frame <-  trial_steer[first(which(trial_steer$autoflag == "FALSE")),]
onset_frame <- (filter(trial_steer, timestamp_trial > first(trial_steer$onsettime)))[1,]
first_frame <- trial_steer[1,]
time_axis <- data.frame(ts = seq.int(0, 15), ts_exp = seq.int(0,15) + first_frame$timestamp_exp)

head(onset_frame)
head(trial_steer)

t_y = .75

leg_v = .22 #vertical spacing
leg_t = -.7 #starting top
leg_l = first_frame$timestamp_exp+13 #left align
leg_h = .32 #space between dot and text
lw = .5
leg_t1 = -.5 #starting top
leg_l1 = first_frame$timestamp_exp+.5

p_timings_noload <- ggplot(trial_steer, aes(x = timestamp_exp, y = sb_mirrored)) + 
  
  
  
  #labels
  geom_text(data = onset_frame, aes( x = timestamp_exp - 1, y = sb_mirrored - .8, label = "Failure onset"), size = ansize) +
  geom_segment(data = onset_frame, aes(x = timestamp_exp - 1, xend = timestamp_exp - .1, y = sb_mirrored -.7, yend = sb_mirrored - .1), colour = "black", size=.75, alpha=1, arrow=arrow(angle = 20, length = unit(0.1, "cm"), type = "closed")) +
  geom_text(data = takeover_frame, aes( x = timestamp_exp - 1, y = sb_mirrored - .6, label = "Takeover"), size = ansize) +
  geom_segment(data = takeover_frame, aes(x = timestamp_exp - 1, xend = timestamp_exp - .1, y = sb_mirrored - .5, yend = sb_mirrored - .1), colour = "black", size=.75, alpha=1, arrow=arrow(angle = 20, length = unit(0.1, "cm"), type = "closed")) +
  
  
  #scale_color_manual(values = c("TRUE" = cols[4], "FALSE" = cols[3])) +
  scale_linetype_manual(values=c("TRUE" = "solid", "FALSE" = "dotted")) +
  guides(linetype = FALSE) +
  #guides(col = FALSE) +
  
  
  
  #time axis
  geom_line(data = time_axis, aes(x = ts_exp, y = 0)) +
  geom_point(data = time_axis[1,], aes(x = ts_exp, y = 0), size = 2) +
  geom_point(data = tail(time_axis,1), aes(x = ts_exp, y = 0), size = 2) +
  geom_text(data = tail(time_axis,1), aes(x = ts_exp, y = -.2, label = paste0(ts, " s")), size = ansize) +
  geom_text(data = head(time_axis,1), aes(x = ts_exp, y = -.2, label = paste0(ts, " s")), size = ansize) +
  geom_segment(data = time_axis, aes(x = ts_exp, y = 0, xend = ts_exp, yend = .05)) +
  
  #steering signal
  geom_path(aes(group = autoflag, linetype = autoflag), col = mycol) +
  geom_point(data = onset_frame, fill = "black", col = "black", shape = 23) +
  geom_point(data = takeover_frame, fill = "black", col = "black", shape = 23) +
  scale_y_reverse(lim = c(.5,-1.5)) +
  theme_classic() +
  

  annotate("segment", x = leg_l-lw, xend = leg_l, y= leg_t, yend = leg_t, col = mycol) +
  annotate("text", x = leg_l+leg_h, y = leg_t, label = "Automation", hjust = 0, vjust = .5, size = ansize) +
    
    annotate("segment", x = leg_l-lw, xend = leg_l, y= leg_t - (1*leg_v), yend = leg_t - (1*leg_v), col = mycol, linetype = "dotted") +
  annotate("text", x = leg_l+leg_h, y = leg_t - (1*leg_v), label = "Manual", hjust = 0, vjust = .5, size = ansize) +

  #remove axis 
  theme(axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank()) 
  
  
print(p_timings_noload)
ggsave("p_methods_timings_noload.eps", plot = p_timings_noload, dev = cairo_ps, width = 13.2, height = 5, units = "cm", dpi = 300)
ggsave("p_methods_timings_noload.svg", plot = p_timings_noload, width = 9, height = 5, units = "cm", dpi = 300)


double_timings <- plot_grid(p_timings_noload, p_timings, ncol = 1, labels = c("A","B"), rel_heights = c(2,2.5))
print(double_timings)
ggsave("p_methods_timings_double.eps", plot = double_timings, dev = cairo_ps, width = 8.7, height = 8, units = "cm", dpi = 300)

ggsave("p_methods_timings_double.svg", plot = double_timings, width = 8.7, height = 10, units = "cm", dpi = 300)



```




